---
title: "Exercise 01 RbasicsT1"
author: "Neisse Niklas_ neisse.n@protonmail.com"
date: "25/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Setting stage

```{r packages}

library(tidyverse)

```

1. create a vector containing the names of 5 tree species

```{r}

species <- c('Thuja plicata','Tsuga canadensis','Pinus aristata','Xanthocyparis nootkatensis','Fagus grandifolia')

```

2. create a vector containing the integers between 2 and 6 by two different R-ways

```{r}

intbet1 <- c(2:6)
intbet2 <-  seq(2,6)

```

3. create a vector containing 5 uniformly distributed random numbers

```{r}

unif1 <- runif(5)

```

4. create a vector containing 5 randomly chosen values between 35 and 77 (uniformlyd istributed), e.g. the tree diameter in breast height

```{r}

unif2 <- runif(5, 35, 77)

```

5. create a vector containing 5 randomly chosen values with arithmetic average of 50 and
standard deviation of 15

```{r}

nrmrmd <- rnorm(5,50,15)

```

6. create a vector with 6 integer numbers

```{r}

int1 <- seq(1,6)

```

7. remove the 6th entry of the vector

```{r}

int1[-6]

```

8. put together the vectors 1, 2, and 5 into a data frame with meaningful column names

```{r}

df1 <- c(data.frame('species' = species, 'id' = intbet1, 'dbh' = nrmrmd))

```

9. put together the vectors 1,2, and 5 into a list

```{r}

lst1 <- c(list('species' = species, 'id' = intbet1, 'dbh' = nrmrmd))

```

10. explore differences between 8. and 9.

There is no difference between object 8. and 9. 
Lists are the most flexible datastructure in R. 
  A colection of elements without any restrictions on the class.
Dataframes are lists with following restrictions:
  - two variables cannot have the same name
  - all elements are vectors
  - all elements have an equal lenght

11. access the diameter of tree 3 in the data frame by two different R-ways

```{r}

df1[[3]][3]

df1 %>% 
  as.tibble %>% 
  filter(id == '3') %>% 
  select(dbh)

```

12. access the dbh vector of the list

```{r}

df1 %>% 
  as.tibble %>% 
  select(dbh)

```

13. access the diameter of the third tree in the list using different R-ways

see 11.

14. multiply all diameters of trees with 1.2, when the diameter is larger than 50 cm by using the ifelse() function

```{r}

df1 %>% 
  as.tibble %>% 
  mutate(dbh1.2 = ifelse(dbh > 50, dbh * 1.2, dbh))

ifelse(df1$dbh > 50, df1$dbh * 1.2, df1$dbh)

```

15. do the same process by using a for-loop and if – else branching

```{r}

 # does't work

for (dbh in df1) {
  if(dbh > 50){dbh = dbh * 1.2} else{dbh = dbh}
}

```

16. program a simple example for a while-loop, a for-loop, and a while-loop, a repeat-loop and try the break command

```{r}


```

17. add a row with a 6th tree species to your data frame

```{r}

df1 %>% 
  as.tibble %>% 
  add_row(species = 'Betula papyrifera')

```

18. create a matrix with random integers between 0 and 1000 with 3 colums and 6 rows

```{r}

m1 <- cbind(as.integer(runif(6,0,1000)),as.integer(runif(6,0,1000)),as.integer(runif(6,0,1000)))

```

