---
title: "HOBO Exercise 2"
author: "Neisse N; neisse.n@protonmail.com"
date: "08/01/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Setting stage

Packages in use

```{r packages, message=FALSE, warning=FALSE}
library(readr)
library(tidyverse)
library(lubridate)
library(rmarkdown)
library(rio)
library(zoo) # rollapply
```

Loading-in data

```{r data upload, message=FALSE, warning=FALSE}
rm(list=ls(all=TRUE))
df <- read_csv("C:/Users/NeoN/Desktop/2020FreiburgEnvironmentalSciences/Semester/Semester1/Data- Storage Collection & Managment/data/raw-data/10347371.csv")
df <- as.tibble(df)
```


## 1. Quality contcol procedure (QCP)

Exploratory data analysis: Graphs

```{r data visualisation, echo=FALSE}
df %>% 
  ggplot(mapping = aes(x = date_time,
                       y = temp,
                       color = temp,
                       fill = temp))  %>% 
  + geom_line() + scale_color_gradient2(low = "darkblue",
  mid = "darkgrey",
  high = "darkred",
  midpoint = 0)

df %>% 
  ggplot(mapping = aes(x = date_time,
                       y = lux,
                       color = lux,
                       fill = lux)) %>% 
  + geom_line() + scale_color_gradient2(low = "black", 
                                         mid = "darkgrey",
                                         high = "darkred",
                                         midpoint = 1000)
```

#### 1.1 Respect to plausible temperature measurement rang of senor

```{r measurement rang}
df <-  df %>%  
  mutate(qc1 = if_else(temp > 70 | temp < -20,1,0)) 
```

#### 1.2 Respect to plausible rate of temperature change (1K)

```{r rate of change}
df <- df %>% 
  mutate(qc2 = if_else(temp - lead(temp) > 1 |temp - lead(temp) < -1 ,1, 0))
```

#### 1.3 Respect to minimum temperature variability (Persistence)

```{r persistence}
df <- df %>% 
  mutate(qc3 = if_else(temp - lag(temp, n = 1) == 0 &
                         temp - lag(temp, n = 2) == 0 &
                         temp - lag(temp, n = 3) == 0 &
                         temp - lag(temp, n = 4) == 0 &
                         temp - lag(temp, n = 5) == 0,
                       1,0, missing = 1))
```
#### 2.4 Respect to light intensity

```{r light intensity}
df <- df %>%
  
  mutate(L1 = if_else(lux > 20000,1, 0)) %>% 
  mutate(L1adj = rollapply(L1, 3, sum, fill= 1)) %>% 
  mutate(qc4 = if_else(L1adj != 0, 1,0)) %>% 
  select(- c(L1, L1adj)) %>% 
  
  mutate(L2 = if_else(lux > 30000,1, 0)) %>% 
  mutate(L2adj = rollapply(L2, 7, sum, fill= 1)) %>% 
  mutate(qc5 = if_else(L2adj != 0, 1, 0)) %>% 
  select(- c(L2, L2adj))
```



```{r lux historgam}
df %>% 
  mutate(p = percent_rank(lux)) %>% 
  ggplot(mapping = aes(x = lux, y = p)) +
  geom_line()
  
  
  
df %>% mutate(p = percent_rank(lux)) %>% 
  tail()
```


## 2. Flagging system

```{r flag}
df <- df %>% 
  rowwise() %>% 
  mutate(
    flag = max(c(qc1, qc2, qc3, qc4, qc5)))
```

```{r hourly flags and averages}
dfh <- df %>%
  mutate(date = date(date_time), .after = 'date_time') %>% 
  mutate(hour = hour(date_time), .after = 'date') %>%
  group_by(date, hour) %>%
  summarise(flag_h = if_else(sum(flag) >1, 1,0), 
            th = ifelse(flag_h != 0, NA, mean(temp))) %>% 
  add_column(date_time = seq(ymd_hm('2020-11-30 00:00'),
                             ymd_hm('2020-12-20 23:00'),
                             by = '1 hour'), 
             .before = 'date') %>% 
  mutate(origin = ifelse(is.na(th), "R", "H")) %>% 
  ungroup()
```

## 3. Regression Model

#### 3.1 Reference sattions

```{r import reference staions}
rs_wbi <- read_delim("C:/Users/NeoN/Desktop/2020FreiburgEnvironmentalSciences/Semester/Semester1/Data- Storage Collection & Managment/data/raw-data/reference stations/WBI Stunde_096.csv",
                    delim = ';',
                    locale=locale(decimal_mark = ","),
                    col_types = cols( 
                      Tag = col_date(format = "%d.%m.%Y"),
                      Stunde = col_time(format = "%H:%M"),
                      AVG_TA200 = col_double()
))
rs_wbi <- rs_wbi %>% rename(date = Tag, hour = Stunde, th = AVG_TA200)
#______________________________________________________________________________
rs_umg <- read_csv("C:/Users/NeoN/Desktop/2020FreiburgEnvironmentalSciences/Semester/Semester1/Data- Storage Collection & Managment/data/raw-data/reference stations/Freiburg_Garten_2020-11-30_2020-12-20.csv")
rs_umg <- rs_umg %>% rename(date_time = UTC, th = `Lufttemperatur (°C)`) %>% 
  select(- Lokalzeit)
#______________________________________________________________________________
rs_dwdfu <- read_delim("C:/Users/NeoN/Desktop/2020FreiburgEnvironmentalSciences/Semester/Semester1/Data- Storage Collection & Managment/data/raw-data/reference stations/produkt_air_temperature_13667_akt.txt", 
                       delim = ";",
                       escape_double = FALSE,
                       col_types = cols(
                         MESS_DATUM = col_datetime(format = "%Y%m%d%H")),
                       trim_ws = TRUE)
rs_dwdfu <- rs_dwdfu %>% rename(date_time = MESS_DATUM,
                    th = LUFTTEMPERATUR) %>%
  select(date_time,th) %>% 
  filter(date_time >= as.Date("2020-11-30"), 
         date_time < as.Date("2020-12-21"))
#______________________________________________________________________________
rs_dwdff <- read_delim("C:/Users/NeoN/Desktop/2020FreiburgEnvironmentalSciences/Semester/Semester1/Data- Storage Collection & Managment/data/raw-data/reference stations/produkt_tu_stunde_20190713_20210112_01443.txt",
                       delim = ";",
                       escape_double = FALSE,
                       col_types = cols(
                         MESS_DATUM = col_datetime(format = "%Y%m%d%H")),
                       trim_ws = TRUE)
rs_dwdff <- rs_dwdff %>% rename(date_time = MESS_DATUM,
                    th = TT_TU) %>%
  select(date_time,th) %>% 
  filter(date_time >= as.Date("2020-11-30"), 
         date_time < as.Date("2020-12-21"))
```

#### 3.2 Regression model

```{r Modeling th, include=FALSE}
model_wbi <- lm(dfh$th ~ rs_wbi$th)
summary(model_wbi)
# R2 = 0.8942
model_umg <- lm(dfh$th ~ rs_umg$th)
summary(model_umg)
# R2 = 0.9231
model_dwdfu <- lm(dfh$th ~ rs_dwdfu$th)
summary(model_dwdfu)
# R2 = 0.8881
model_dwdff <- lm(dfh$th ~ rs_dwdff$th)
summary(model_dwdff)
# R2 = 0.7705
```

#### 3.3 Relationship - HOBO and reference station

```{r Any NAS}

dfh_umg <- dfh %>%  
  mutate(th = ifelse(is.na(th),
         predict(model_umg,
                 newdata = rs_umg),
         th)) %>%
  select(date_time, th, origin) %>% 
  rename(date = date_time)
any(is.na(dfh_umg$th))

```

```{r final data exploration}

dfh_umg %>% 
  ggplot(mapping = aes(x = date,
                       y = th,
                       color = th,
                       fill = th)) %>% 
  + geom_line() + scale_color_gradient2(low = "blue",
  mid = "black",
  high = "red",
  midpoint = 0)
```


## 4. Hourly series


```{r uploading data into github}
#write.csv(dfh_umg,
#          'C:/Users/NeoN/Desktop/2020FreiburgEnvironmentalSciences/Semester/Semester1/Data- Storage Collection & Managment/data/10347371_TH.csv', row.names = FALSE , quote=F)
```


